Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-19 tex/Main Text/manuscript.tex
更新过渡阶段的图注释

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shift of coupled systems can be caused by gradual or abrupt changes, 
where anthropogenic stresses are among the most important drivers of. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
With the accumulation of human interventions, 
a natural-social binary structure of the water cycle has emerged, 
dominating the current feedbacks of the human-water systems.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, 
regime shifts as transitional phases of water utilization regimes, 
similar to evolution of social-ecological system, 
is one of the most important characteristics towards natural-social binary structure.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes, 
which conceptualizes a general trajectory towards a natural-social binary water cycle (figure \ref{fig:framework}).

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Transition framework of the water utilization regime.}
	tet
	\label{fig:framework}
\end{figure*}

% 在水循环向二元系统过渡过程中，存在几个明显的特征。
Towards natural-social binary cycle, there are two obvious features between different transition phases.
% 阶段1
From the first phase (natural cycle) (Figure~\ref{fig:framework}a), 
water is a kind of direct provisioning resources, mainly supporting to crop, livestocks or human-beings, 
as basic ecological services.
% 阶段2
However, to the second phase (local binary cycle) (Figure~\ref{fig:framework}b), 
as local socio-economic systems developing, 
industry and services (secondary and tertiary-industry) calling for further water consumptions.
However, since their services can only be generated through the circulation of socio-economic systems, 
water resources play a non-provisioning role in this cycle. 
What's more, better organized socio-economic system and developed technology 
gives humans the will and ability to better manage water resources and change, 
with intensive intervention in the natural water cycle. 
% 阶段3
Entering the third phase (basin binary cycle) (Figure~\ref{fig:framework}c), 
with further growth in more economically efficient industries and services, 
trade-off between whose water demands with provisioning demands 
should be based on the needs of regional socio-economic systems.
What's more, Water withdrawals are no longer simply determined by local economic development, 
but more so by the socio-economic development needs of the entire basin, 
while water resource management are also more often considered on a basin-wide basis, correspondingly.

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards binary water cycle, 
three dimensions of water utilization regime are various, following three laws of evolution respectively.
Firstly, although stresses on water resources increases by economic expansion boosting water demands, 
socio-economic progress responding to resource scarcity because of better management and increased water use efficiency. 
For Example...
Secondly, the non-provisioning part of water demands further growths and 
tendentiousness of water utilization continually changes, 
as humans are more dependent on benefits from non-provisioning part of water supply.
Thirdly, With closer socio-economic ties between regions and between regions and river basins, 
the geographic scope of resource supply and demand allocation is expanding, 
leading to changing patterns of water utilization.
By combining the three dimensions, water utilization regimes have a tendency of transitional evolution.

>>>>

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shift of coupled systems can be caused by gradual or abrupt changes, 
where anthropogenic stresses are among the most important drivers of. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
With the accumulation of human interventions, 
a natural-social binary structure of the water cycle has emerged, 
dominating the current feedbacks of the human-water systems.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, 
regime shifts as transitional phases of water utilization regimes, 
similar to evolution of social-ecological system, 
is one of the most important characteristics towards natural-social binary structure.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes, which conceptualizes a general trajectory towards a natural-social binary water cycle.

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{
		Transition framework of the water utilization regime towards natural-social binary cycle.
		\textbf{A. Natural cycle:} As a kind of direct provisioning resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local binary cycle:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions.
		However, as their ecological services generated through the socio-economic cycle, water resources play a non-provisioning role. What's more, better organized socio-economic system and developed technology gives humans the will and ability to better manage water resources and change since this phase, with intensive intervention in the natural water cycle. 
		\textbf{C. Basin binary cycle:} Entering this phase, with further developing in more economically efficient industries and services, trade-off between whose water demands with provisional water demands becomes prominent. Rather than determined by local socio-economic systems, water withdrawals and management act as considerations within the entire basin more, therefore. 
	}
	\label{fig:framework}
\end{figure*}

% 在水循环向二元系统过渡过程中，存在几个明显的特征。
Towards natural-social binary cycle, there are two obvious features between different transition phases  (figure \ref{fig:framework}).
% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards binary water cycle, 
three dimensions of water utilization regime are various, following three laws of evolution respectively.
Firstly, although stresses on water resources increases by economic expansion boosting water demands, 
socio-economic progress responding to resource scarcity because of better management and increased water use efficiency. 
For Example...
Secondly, the non-provisioning part of water demands further growths and 
tendentiousness of water utilization continually changes, 
as humans are more dependent on benefits from non-provisioning part of water supply.
Thirdly, With closer socio-economic ties between regions and between regions and river basins, 
the geographic scope of resource supply and demand allocation is expanding, 
leading to changing patterns of water utilization.
By combining the three dimensions, water utilization regimes have a tendency of transitional evolution.
